Data exploration

### 2021-08-24 ms/data_exploration.Rmd
Update data_exploration.Rmd

# Make biodiversity metrics dataframe with centroid of each site for models
  biodiv_ferns_cent <- 
    biodiv_ferns_spatial %>%
    # keep only variables needed for model and only rows with zero missing data
    filter_data_for_model(c("grids", "lat", "long", resp_vars_env, indep_vars)) %>%
    sf::st_set_geometry(NULL) %>%
    as_tibble()
```

>>>>

# Make biodiversity metrics dataframe with centroid of each site for models
  biodiv_ferns_cent <- 
    biodiv_ferns_spatial %>%
    # drop geometry (only need centroids for modeling)
    st_set_geometry(NULL) %>%
    # keep only variables needed for model and only rows with zero missing data
    select(all_of(c("grids", "lat", "long", resp_vars_env, indep_vars))) %>%
    ggplot2::remove_missing() %>%
    as_tibble()
```
